---
title: "Player Scrape"
author: "Logan Clarke"
date: "3/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Steps:

1. Gather all the team ids
2. Set up a for loop. For each iteration (team id), it will open the link
3. Scrape both tables from each team
4. rbind all the players and teams into a table
5. join the tables by team name
6. get rid of rows with team name (if applicable)
7. rearrange columns if necessary to match model
8. run the model for each row in the dataframe and save it as a new column
9. filter this dataframe based on which players are included in the transfer portal
10. filter that dataframe based on any credentials from Melanie


Scraping the links
```{r}
library(rvest)
#url information
url <- "https://www.espn.com/womens-college-basketball/teams"
all_teams_code <- read_html(URL)

#these are the links of the different teams - second argument found with inspector gadget
links <- html_nodes(all_teams_code, '.n9:nth-child(1) .AnchorLink') %>% 
  html_attr("href")

links1 <- paste0("https://www.espn.com", links)

links1[1]


#this gets the url for everything in the list
all_urls <- lapply(links1, read_html)

```



Function to extract every single table

```{r}
table_func <- function(link){
  #read in the link
  html <- read_html(link)
  
  #extract the link
  extracted_tables <- html_nodes(html, '.remove_capitalize') %>% 
    html_table(fill = T)
  
  #this is the first table on the page
  table_1 <- extracted_tables[1]
  
  #change it into a dataframe from a list
  table_1a <- data.frame(table_1)
  
  #it pasted the stats below the names. We want to find the total row, split the dataframe in two at that point, and then bind the two dataframes together
  which(grepl("Total", table_1a$Name))
  
  split_tables <- split(table_1a, cumsum(1:nrow(table_1a) %in% which(grepl("Total", table_1a$Name))))
  
  #let's clean up the name table
  names <- data.frame(split_tables[1]) %>% 
    mutate(Name = X0.Name) %>% 
    select(Name)
  
  #Cleaning up the stats table: getting rid of the blank total row, setting the new first row to be column names, and then deleting the total row at the bottom
  stats <- data.frame(split_tables[2])[-1,] %>% 
    row_to_names(row_number = 1) %>% 
    slice(1:(n() - 1))
  
  #now that the two tables are the same length, we can bind them together
  both_tables <- cbind(names, stats)
  
  #now to repeat the process with the second table!
  
  #this is the first table on the page
  table_2 <- extracted_tables[2]
  
  #change it into a dataframe from a list
  table_2a <- data.frame(table_2)
  
  #it pasted the stats below the names. We want to find the total row, split the dataframe in two at that point, and then bind the two dataframes together
  which(grepl("Total", table_2a$Name))
  
  split_tables2 <- split(table_2a,cumsum(1:nrow(table_2a) %in% which(grepl("Total", table_2a$Name))))
  
  #let's clean up the name table
  names2 <- data.frame(split_tables2[1]) %>% 
    mutate(Name = X0.Name) %>% 
    select(Name)
  
  #Cleaning up the stats table: getting rid of the blank total row, setting the new first row to be column names, and then deleting the total row at the bottom
  stats2 <- data.frame(split_tables2[2])[-1,] %>% 
    row_to_names(row_number = 1) %>% 
    slice(1:(n() - 1))
  
  #now that the two tables are the same length, we can bind them together
  both_tables2 <- cbind(names2, stats2)
  
  
  #Let's clean up the names on them
  
  names(both_tables) <- c("Name", "GP", "MPG", "PPG", "REBPG", "ASTPG", "STLPG", "BLKPG", "TOPG", "FG%", "FT%", "3P%")
  
  names(both_tables2) <- c("Name", "TMIN", "FGM", "FGA", "FTM", "FTA", "3PM", "3PA", "PTS", "OR", "DR", "TREB", "AST",
                           "TO", "STL", "BLK")
  
  
  #now join the two tables together on name
  all_tables <- both_tables %>% 
    full_join(both_tables2)
  
  return(all_tables)
}

table_func(links1[17])



```


Apply the function to the list of links

```{r}
tables_list <- lapply(links1, table_func)
```


Comnbine all the dataframes into one big guy

```{r}
library(tidyverse)
full_data <- bind_rows(tables_list, .id = "column_label") %>% 
  select(-column_label)

write_csv(full_data, "full_stats.csv")
```



Appendix - previous attempts

Scraping the tables from one link and combining them into one table
```{r}

#attempt 1 at collecting the tables
tables1 <- html_nodes(all_urls[1], '.remove_capitalize') %>% 
  html_table(fill = TRUE)

#attempt 2 of collecting the tables
table2s <- url1 %>% 
  html_node("table") %>% 
  html_table(fill = TRUE)

#let's simplify and try with just one url

bellarmine_link <- links1[1]

bell_html <- read_html(bellarmine_link)

bell_tables <- html_nodes(bell_html, '.remove_capitalize') %>% 
  html_table(fill = T)

#this is the first table on the page
bell_1 <- bell_tables[1]

#change it into a dataframe from a list
bell_1a <- data.frame(bell_1)

#it pasted the stats below the names. We want to find the total row, split the dataframe in two at that point, and then bind the two dataframes together
which(grepl("Total", bell_1a$Name))

split_tables <- split(bell_1a,cumsum(1:nrow(bell_1a)%in%which(grepl("Total", bell_1a$Name))))

#let's clean up the name table
names <- data.frame(split_tables[1]) %>% 
  mutate(Name = X0.Name) %>% 
  select(Name)

#Cleaning up the stats table: getting rid of the blank total row, setting the new first row to be column names, and then deleting the total row at the bottom
library(janitor)
stats <- data.frame(split_tables[2])[-1,] %>% 
  row_to_names(row_number = 1) %>% 
  slice(1:(n() - 1))

#now that the two tables are the same length, we can bind them together
both_tables <- cbind(names, stats)

#now to repeat the process with the second table!

#this is the first table on the page
bell_2 <- bell_tables[2]

#change it into a dataframe from a list
bell_2a <- data.frame(bell_2)

#it pasted the stats below the names. We want to find the total row, split the dataframe in two at that point, and then bind the two dataframes together
which(grepl("Total", bell_2a$Name))

split_tables2 <- split(bell_2a,cumsum(1:nrow(bell_2a)%in%which(grepl("Total", bell_2a$Name))))

#let's clean up the name table
names2 <- data.frame(split_tables2[1]) %>% 
  mutate(Name = X0.Name) %>% 
  select(Name)

#Cleaning up the stats table: getting rid of the blank total row, setting the new first row to be column names, and then deleting the total row at the bottom
stats2 <- data.frame(split_tables2[2])[-1,] %>% 
  row_to_names(row_number = 1) %>% 
  slice(1:(n() - 1))

#now that the two tables are the same length, we can bind them together
both_tables2 <- cbind(names2, stats2)


#Let's clean up the names on them

names(both_tables) <- c("Name", "GP", "MPG", "PPG", "REBPG", "ASTPG", "STLPG", "BLKPG", "TOPG", "FG%", "FT%", "3P%")

names(both_tables2) <- c("Name", "TMIN", "FGM", "FGA", "FTM", "FTA", "3PM", "3PA", "PTS", "OR", "DR", "TREB", "AST",
                        "TO", "STL", "BLK")


#now join the two tables together on name
all_tables <- both_tables %>% 
  full_join(both_tables2)

```
